Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-06-26 paper/agujournaltemplate.tex
Modify Figure 4

\begin{abstract}
Tectonic tremor has been explained as a swarm of low-frequency earthquakes, which are located on a narrow fault at the plate boundary. However, due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source and the distance of the source to the plate interface with great precision. The thickness of the tremor region is also not well constrained. The tremor may be located on a narrow fault as the low-frequency earthquakes appear to be, or distributed over a few kilometers wide low shear-wave velocity layer in the upper oceanic crust, which is thought to be a region with high pore-fluid pressure. Lag times of peaks in the cross-correlation of the horizontal and vertical components of tremor seismograms, recorded by small-aperture arrays in the Olympic Peninsula, Washington, are interpreted to be S minus P times.  Tremor depths are estimated from these S minus P times using epicenters from a tremor catalog. The tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick and is very close to the depths of low-frequency earthquakes. The tremor is distributed over a wider depth range than the low-frequency earthquakes. However, due to the uncertainty on the depth, it is difficult to conclude whether the source of the tremor is located at the top of the subducting oceanic crust, in the lower continental crust just above the plate boundary, or in a narrow zone at the plate boundary.
\end{abstract}

@@

Tremor is a long (several seconds to many minutes), low amplitude seismic signal, with emergent onsets, and an absence of clear impulsive phases. Tectonic tremor has been explained as a swarm of small, low-frequency earthquakes (LFEs) ~\cite{SHE_2007_nature}, that is small magnitude earthquakes (M $\sim$ 1) where frequency content (1-10 Hz) is lower than for ordinary small earthquakes (up to 20 Hz). The source of the LFEs is located on the plate boundary, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL, ROY_2014}. Due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source with the same precision. The tremor source is assumed to be located close to the plate boundary. In subduction zones such as Nankai and Cascadia, tectonic tremor observations are spatially and temporally correlated with slow slip observations ~\cite{OBA_2002, ROG_2003}. Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS). \\

The occurrence of tremor seems to be linked to low effective normal stress or high fluid pressure near the location of the tremor. Indeed, ~\citeA{SHE_2006} have observed a high P-wave to S-wave velocity ratio in the subducting oceanic crust near the location of the LFEs in western Shikoku, Japan. In Cascadia, ~\citeA{AUD_2009} have computed teleseismic receiver functions in Vancouver Island, and analyzed the delay times between the forward-scattered P-to-S, and back-scattered P-to-S and S-to-S conversions at two seismic reflectors identified as the top and bottom of the oceanic crust. It allowed them to compute the P-to-S velocity ratio of the oceanic crust layer and the S-wave velocity contrast at both interfaces. The very low Poisson's ratio of the layer could not be explained by the mineral composition, and they interpreted it as evidence for high pore-fluid pressure. The link between tremor and high pore fluid pressure is also supported by the influence of tidal cycles on the variations of tremor occurrence. \citeA{NAK_2008} noticed that tremor swarms often exhibit occurrences with a periodicity of about 12 or 24 h, and concluded that they are probably related to Earth tides. Their occurrence is also well correlated with time evolution of Coulomb failure stress (CFS) and CFS rate. However, they noted that tremor occurrences are advanced by a few hours relative to CFS, from which they conclude that a simple Coulomb threshold model is not sufficient to explain tremor occurrence. Instead they point out that the correlation of tremor occurrence and the CFS rate as well as the time delay between both could be reproduced by using the rate- and state-dependent friction law. ~\citeA{THO_2009} have also observed that tremor occurrence on the deep San Andreas fault are correlated with small, tidal shear stress changes. They explain it by a very weak fault zone with low effective normal stress, probably due to near-lithostatic pore pressures at the depth of the tremor source region. \\

@@

Whereas the position of the subduction zone ETS does not seem to coincide with a specific temperature or dehydration reaction ~\cite{PEA_2009}, there seems to be a good coincidence between the location of the fore-arc mantle corner, and the location of ETS ~\cite{HYN_2015}. The generation of slow slip and tectonic tremor could then be related to the presence of quartz in the overriding continental crust. Using receiver functions of teleseismic body waves, and data from the literature, ~\citeA{AUD_2014} observed that the recurrence time of slow earthquakes increases linearly with the Vp / Vs ratio of the forearc crust. They also noticed that along a margin-perpendicular profile from northern Cascadia, the Vp / Vs ratio of the forearc, and the recurrence time of ETS events, decrease with increasing depth. Likewise, ~\citeA{HYN_2015}  pointed out that the deep fore-arc crust has a very low Poisson's ratio (less than 0.22), and that the only mineral with a very low Poisson's ratio is quartz (about 0.1), which led them to conclude that there may be a significant amount of quartz (about 10\% in volume) in the deep fore-arc crust above the fore-arc mantle. ~\citeA{AUD_2014} explained the presence of quartz in the forearc by the enrichment of forearc minerals in fluid-dissolved silica derived from the dehydration of the down-going slab. As the solubility of silica increases with temperature, fluids generated at depth and rising up the subduction channel should be rich in silica ~\cite{HYN_2015}. \\

@@

Moreover, the zone with high low Poisson's ratio observed by ~\citeA{HYN_2015} has a large vertical extent (about 10 kilometers). If the whole zone is associated with quartz deposition and tectonic tremor generation, we should also observe a large vertical distribution of the source of the tremor. ~\citeA{KAO_2006} have used a Source Scanning Algorithm to detect and locate tremor, and have indeed located tremor in the continental crust, with a wide depth range of over 40 km. They noted that this wide depth range could not arise from either analysis uncertainties or a systematic bias in the velocity model they used. Uncertainties on the location of the tremor have been estimated by  ~\citeA{IDE_2012} at about 1.5 km in epicenter and 4.5 km in depth. A follow-up study by ~\citeA{KAO_2009} gave a thickness of the tremor zone of 5-10 km. This depth range is inconsistent with the depth of the LFEs, which have been located on a thin band at or near the plate interface with a rupture mechanism that corresponds to the thrust dip angle ~\cite{IDE_2007_GRL}. In the Olympic Peninsula, LFE families have been identified and located by ~\citeA{CHE_2017_JGR}, and all LFE families were located near the plate interface. Further study is thus needed to narrow the uncertainty on the depth of the source of the tremor, and verify whether tremor could occur in a wider zone than LFEs. \\

@@

A second method is based on the assumption that repeating tremor or LFEs with sources located nearby in space will have similar waveforms ~\cite{BOS_2012, ROY_2014, SHE_2006, SHE_2007_nature}. For instance, ~\citeA{BOS_2012} looked for LFEs by computing autocorrelations of 6-second long windows for each component of 7 stations in Vancouver Island. They then classified their LFE detections into 140 families. By stacking all waveforms of a given family, they obtained an LFE template for each family. They extended their templates by adding more stations and computing cross-correlations between station data and template waveforms. They used P- and S-traveltime picks to obtain an hypocenter for each LFE template. By observing the polarizations of the P- and S-waveforms of the LFE templates, they computed focal mechanisms and obtained a mixture of strike slip and thrust mechanisms, corresponding to a compressive stress field consistent with thrust faulting parallel to the plate interface. Further study showed that the average double couple solution is generally consistent with shallow thrusting in the direction of plate motion \cite{ROY_2014}. \\

@@

In this study, we extend on the method used by ~\citeA{LAR_2009} using the cross-correlation between horizontal and vertical components of seismic recordings to estimate the depth of the source of the tectonic tremor, and the depth extent of the region from which tremor originates. If indeed tremor is made of swarms of LFEs, and both represent the regions of deformation during ETS events, we would expect the thickness of the tremor to be the same as the thickness of the LFEs. If not, tremor may be occurring where LFEs are harder to detect because either smaller in amplitude, or spread out over continuous space and not as clearly repeating.

@@

The analysis we carried out above may not lead to a reliable value of the depth of the source of the tremor for all relative positions of the array and the tremor. First, some areas are badly covered, and only a few tremor or no tremor at all were recorded. We limit our analysis to grid cells where there are at least 30 one-minute-long time windows in the best cluster. Second, the method works best for nearly vertical ray paths. A third problem is that we assumed that the location of the tremor source is fixed during the one-minute-long time window where we compute the cross-correlation of the seismic signal. However, during an ETS event, rapid tremor streaks have been observed to propagate up-dip or down-dip at velocities ranging on average between 30 and 110 km/h ~\cite{GHO_2010_G3}, which corresponds to a maximum source displacement of 0.9 km updip or downdip during the 30 seconds duration before and after the middle of the time window. The change in predicted S-minus-P time caused by changing source location by 0.9 km in the up- or down-dip direction is small for tremor along strike from the array or in the down dip direction.  However, the change in this lag time for tremor sources up-dip from the arrays exceeds one quarter of the dominant period of the tremor signal (period= 0.33 s) for tremor sources more than 18 km updip from an array. Thus, tremors beyond 18 km updip of an array may not add coherently during rapid tremor migrations. This method works best if the P-wave is cleanly recorded on the vertical component and the S-wave on the horizontals, so generally speaking the results are more robust for vertical ray paths. \\

Finally, the data from some of the arrays are very noisy, which makes it hard to see a signal emerging when stacking over the one-minute-long time windows. We chose to keep only the locations for which the ratio between the maximum value of the stack of the envelopes of the cross-correlation functions to the root mean square is higher than 5. We compute the root mean square of the cross-correlation for a time lag between 12 and 14s because we do not expect any reflected wave to arrive that late after a direct wave. The corresponding stack of the envelopes of the cross-correlation functions are shown in Figure 4 for the East-West component and the North-South component. The grey vertical line shows the theoretical time lag between the arrival of the direct P-wave and the arrival of the direct S-wave using the corresponding 1D velocity model for this array and the plate boundary model from ~\citeA{MCC_2006}, the dashed line corresponds to the slab model from ~\citeA{PRE_2003}. There is a good agreement between the timing of the peak and the theoretical time lag for most of the locations of the source of the tremor. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1cm},clip]{figures/BS_PWS_PWS_0.eps}
\caption{Stack of the envelopes of the cross-correlation signals for different positions of the tremor source relative to the Big Skidder array showing the cross-correlation between the East-West and the vertical components (red lines) and between the North-South and vertical components (blue lines). The theoretical S-minus-P times (grey plain line for the McCrory model, grey dashed line for the Preston model) are generally in good agreement with the peaks in cross-correlation functions. The location of the tremor varies from west to east (left to right) and from south to north (bottom to top). The numbers next to each graph indicate the number of one-minute-long time windows in the best cluster. For clarity, we plotted only the part of the cross-correlation signal corresponding to timelags between 2 and 8 seconds.}
\label{pngfiguresample}
\end{figure}

We considered only the horizontal component with the maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the theoretical time lag if the source of the tremor was located on the plate boundary. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. We did the same analysis for the eight arrays of the experiment. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. In the following, we did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

To estimate the uncertainty on the depth of the source of the tremor, we computed the width of the stack of the envelopes of the cross-correlation functions at half the maximum of the peak. We then computed the associated depth difference using the 1D velocity model. As we computed the envelopes of the cross-correlation functions before stacking, the peak is large and also the associated uncertainty on the depth. Nevertheless, about 75\% of the data points have an uncertainty under 8km (Figure 5). The uncertainties are higher for the Burnt Hill array, and are almost always lower than 8km for the five other arrays. We tried different stacking methods, both for the stacking of the correlation functions over all the seismic stations of a given array, and for the stacking of the envelopes of those stacks over the one-minute-long time windows when tremor is detected. We experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack, and found that using a phase-weighted stack for both the stacking over the stations and the stacking over one-minute-long time windows gave the lower uncertainty on the depth of the source of the tremor. \\

@@

In the following, we kept only the data points for which the maximum amplitude of the stack is higher than 0.05. Figures 6 and 7 show respectively a map and several cross-sections of the depth of the source of the tremor. Figure 8 shows a map of the distance between the source of the tremor and the plate boundary from the Preston model, alongside with the depth of the low-frequency earthquake families observed by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}. There is a good agreement between the depth of the source of the tremor, the depth of the low-frequency earthquake families, and the depth of the plate boundary. On the cross-section figures, we compare the distance of the source of the tremor to the plate boundary for different locations of the cross-section. We note that the depth of the tremor matches well the depth of the low-frequency earthquakes. \\

@@

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor is larger than the depth range of the low-frequency earthquakes, but it may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes look closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR} to locate the low-frequency earthquake families. \\

@@

We developed a method to estimate the depth of the source of the tectonic tremor, and the depth extent of the region from which the tremor originates, using S minus P times determined from lag times of stacked cross-correlations of horizontal and vertical components of seismic recordings from small aperture arrays in the Olympic Peninsula, Washington. We found that the source of the tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick. The source of the tremor is thus distributed over a wider depth range than the low-frequency earthquakes. However, due to the depth uncertainty, it is difficult to conclude whether the tremor is located in the subducting oceanic crust, in the lower continental crust just above the plate boundary, or in a layer distributed above and under the plate boundary. The relative location of the source of the tremor compared to the low-velocity layer also observed near the plate boundary also remains uncertain.

@@

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/timelags}.

>>>>

\begin{abstract}
Tectonic tremor has been explained as a swarm of low-frequency earthquakes, which are located on a narrow fault at the plate boundary. However, due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source and the distance of the source to the plate interface with great precision. The thickness of the tremor region is also not well constrained. The tremor may be located on a narrow fault as the low-frequency earthquakes appear to be, or distributed over a few kilometers wide low shear-wave velocity layer in the upper oceanic crust, which is thought to be a region with high pore-fluid pressure. Lag times of peaks in the cross-correlation of the horizontal and vertical components of tremor seismograms, recorded by small-aperture arrays in the Olympic Peninsula, Washington, are interpreted to be S minus P times.  Tremor depths are estimated from these S minus P times using epicenters from a previous study using a multibeam backprojection method. The tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick and is very close to the depths of low-frequency earthquakes. The tremor is distributed over a wider depth range than the low-frequency earthquakes. However, due to the uncertainty on the depth, it is difficult to conclude whether the source of the tremor is located at the top of the subducting oceanic crust, in the lower continental crust just above the plate boundary, or in a narrow zone at the plate boundary.
\end{abstract}

@@

Tremor is a long (several seconds to many minutes), low amplitude seismic signal, with emergent onsets, and an absence of clear impulsive phases. Tectonic tremor has been explained as a swarm of small, low-frequency earthquakes (LFEs) ~\cite{SHE_2007_nature}, that is small magnitude earthquakes (M $\sim$ 1) where frequency content (1-10 Hz) is lower than for ordinary small earthquakes (up to 20 Hz). The source of the LFEs is located on or near the plate boundary, and their focal mechanisms represent shear slip on a low-angle thrust fault dipping in the same direction as the plate interface ~\cite{IDE_2007_GRL, ROY_2014}. The polarization of tremor in northern Cascadia is also consistent with slip on the pate boundary in the direction of relative plate motion ~\cite{WEC_2007}.  Due to the lack of clear impulsive phases in the tremor signal, it is difficult to determine the depth of the tremor source with the same precision. In subduction zones such as Nankai and Cascadia, tectonic tremor observations are spatially and temporally correlated with geodetically observed slow slip  ~\cite{OBA_2002, ROG_2003}. Due to this correlation, these paired phenomena have been called Episodic Tremor and Slip (ETS). \\

The occurrence of tremor seems to be linked to low effective normal stress or high fluid pressure near the location of the tremor. Indeed, ~\citeA{SHE_2006} have observed a high P-wave to S-wave velocity ratio in the subducting oceanic crust near the location of the LFEs in western Shikoku, Japan. In Cascadia, ~\citeA{AUD_2009} have computed teleseismic receiver functions in Vancouver Island, and analyzed the delay times between the forward-scattered P-to-S, and back-scattered P-to-S and S-to-S conversions at two seismic reflectors identified as the top and bottom of the oceanic crust. It allowed them to compute the P-to-S velocity ratio of the oceanic crust layer and the S-wave velocity contrast at both interfaces. The very low Poisson's ratio of the layer could not be explained by the mineral composition, and they interpreted it as evidence for high pore-fluid pressure. The link between tremor and high pore fluid pressure is also supported by the influence of tidal cycles on the variations of tremor occurrence. \citeA{NAK_2008} noticed that tremor swarms often exhibit occurrences with a periodicity of about 12 or 24 h, and concluded that they are probably related to Earth tides. Their occurrence is also well correlated with time evolution of Coulomb failure stress (CFS) and CFS rate. However, tremor occurrences are advanced by a few hours relative to CFS, from which they conclude that a simple Coulomb threshold model is not sufficient to explain tremor occurrence. This discrepancy can be explained by using a rate- and state-dependent friction law. ~\citeA{THO_2009} have also observed that tremor occurrence on the deep San Andreas fault are correlated with small, tidal shear stress changes. They explain it by a very weak fault zone with low effective normal stress, probably due to near-lithostatic pore pressures at the depth of the tremor source region. \\

@@

Whereas the position of the subduction zone ETS does not seem to coincide with a specific temperature or dehydration reaction ~\cite{PEA_2009}, there seems to be a good coincidence between the location of the fore-arc mantle corner, and the location of ETS ~\cite{HYN_2015}. The generation of slow slip and tectonic tremor could then be related to the presence of quartz in the overriding continental crust. Using receiver functions of teleseismic body waves, and data from the literature, ~\citeA{AUD_2014} observed that the recurrence time of slow earthquakes increases linearly with the Vp / Vs ratio of the forearc crust. They also noticed that along a margin-perpendicular profile from northern Cascadia, the Vp / Vs ratio of the forearc, and the recurrence time of ETS events, decrease with increasing depth. Likewise, ~\citeA{HYN_2015}  pointed out that the deep fore-arc crust has a very low Poisson's ratio (less than 0.22), and that the only mineral with a very low Poisson's ratio is quartz (about 0.1), which led them to conclude that there may be a significant amount of quartz (about 10\% by volume) in the deep fore-arc crust above the fore-arc mantle. ~\citeA{AUD_2014} explained the presence of quartz in the forearc by the enrichment of forearc minerals in fluid-dissolved silica derived from the dehydration of the down-going slab. As the solubility of silica increases with temperature, fluids generated at depth and rising up the subduction channel should be rich in silica ~\cite{HYN_2015}. \\

@@

Moreover, the zone with high low Poisson's ratio observed by ~\citeA{HYN_2015} has a large vertical extent (about 10 kilometers). If the whole zone is associated with quartz deposition and tectonic tremor generation, we should also observe a large vertical distribution of the source of the tremor. ~\citeA{KAO_2006} have used a Source Scanning Algorithm to detect and locate tremor, and have indeed located tremor in the continental crust, with a wide depth range of over 40 km. They noted that this wide depth range could not arise from either analysis uncertainties or a systematic bias in the velocity model they used. Uncertainties on the location of the tremor have been estimated by  ~\citeA{IDE_2012} at about 1.5 km in epicenter and 4.5 km in depth. A follow-up study by ~\citeA{KAO_2009} gave a thickness of the tremor zone of 5-10 km. This depth range is inconsistent with the depth of the LFEs, which have been located on a thin band at or near the plate interface with a rupture mechanism that corresponds to the thrust dip angle ~\cite{IDE_2007_GRL}. In the Olympic Peninsula, LFE families have been identified and located by ~\citeA{CHE_2017_JGR}, and all LFE families were located near the plate interface. Further study is thus needed to narrow the uncertainty on the depth of the source of the tremor, and verify whether tremor occurs in a wider zone than LFEs. \\

@@

A second method is based on the assumption that repeating tremor or LFEs with sources located nearby in space will have similar waveforms ~\cite{BOS_2012, ROY_2014, SHE_2006, SHE_2007_nature}. For instance, ~\citeA{BOS_2012} looked for LFEs by computing autocorrelations of 6-second long windows for each component of 7 stations in Vancouver Island. They then classified their LFE detections into 140 families. By stacking all waveforms of a given family, they obtained an LFE template for each family. They extended their templates by adding more stations and computing cross-correlations between station data and template waveforms. They used P- and S-travel-time picks to obtain a hypocenter for each LFE template. By observing the polarizations of the P- and S-waveforms of the LFE templates, they computed focal mechanisms and obtained a mixture of strike slip and thrust mechanisms, corresponding to a compressive stress field consistent with thrust faulting parallel to the plate interface. Further study showed that the average double couple solution is generally consistent with shallow thrusting in the direction of plate motion \cite{ROY_2014}. \\

@@

In this study, we extend on the method used by ~\citeA{LAR_2009} using the cross-correlation between horizontal and vertical components of seismic recordings to estimate the depth of the source of the tectonic tremor, and the depth extent of the region from which tremor originates. If indeed tremor is made of swarms of LFEs, and both represent the regions of deformation during ETS events, we would expect the thickness of the tremor to be the same as the thickness of the LFEs. If not, tremor may be occurring where LFEs are harder to detect because they are either smaller in amplitude, or spread out over continuous space and not as clearly repeating.

@@

To obtain robust results, we limit our analysis to grid cells where there are at least 30 one-minute-long time windows in the best cluster. We assumed that the location of the tremor source is fixed during the one-minute-long time window where we compute the cross-correlation of the seismic signal. However, during an ETS event, rapid tremor streaks have been observed to propagate up-dip or down-dip at velocities ranging on average between 30 and 110 km/h ~\cite{GHO_2010_G3}, which corresponds to a maximum source displacement of 0.9 km updip or downdip during the 30 seconds duration before and after the middle of the time window. The change in predicted S-minus-P time caused by changing source location by 0.9 km in the up- or down-dip direction is small for tremor along strike from the array or in the down dip direction.  However, the change in this lag time for tremor sources up-dip from the arrays exceeds one quarter of the dominant period of the tremor signal (period= 0.33 s) for tremor sources more than 18 km updip from an array. Thus, tremors beyond 18 km updip of an array may not add coherently during rapid tremor migrations. This method works best if the P-wave is cleanly recorded on the vertical component and the S-wave on the horizontals, so generally speaking the results are more robust for near vertical ray paths. \\

Finally, the data from some of the arrays are very noisy, which makes it hard to see a signal emerging when stacking over the one-minute-long time windows. We chose to keep only the locations for which the ratio between the maximum value of the stack of the envelopes of the cross-correlation functions to the root mean square is higher than 5. We compute the root mean square in cluster 1 for a time lag between 12 and 14s because we do not expect any reflected wave to arrive that late after a direct wave. The corresponding stack of the envelopes of the cross-correlation functions are shown in Figure 4 for the East-West component and the North-South component. The grey vertical line shows the theoretical time lag between the arrival of the direct P-wave and the arrival of the direct S-wave using the corresponding 1D velocity model for this array and the plate boundary model from ~\citeA{MCC_2006}, the dashed line corresponds to the slab model from ~\citeA{PRE_2003}. There is a good agreement between the timing of the peak and the theoretical time lag for most of the locations of the source of the tremor. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1cm},clip]{figures/BS_PWS_PWS_0.eps}
\caption{Stack of the envelopes of the cross-correlation signals for different positions of the tremor source relative to the Big Skidder array showing the cross-correlation between the East-West and the vertical components (red lines) and between the North-South and vertical components (blue lines). The theoretical S-minus-P times (grey dashed line for the Preston model) are generally in good agreement with the peaks in cross-correlation functions (grey solid line). The location of the tremor varies from west to east (left to right) and from south to north (bottom to top). The numbers next to each graph indicate the number of one-minute-long time windows in the best cluster. For clarity, we plotted only the part of the cross-correlation signal corresponding to timelags between 2 and 8 seconds.}
\label{pngfiguresample}
\end{figure}

We considered only the horizontal component with the maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the theoretical time lag if the source of the tremor was located on the plate boundary. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. We did the same analysis for the eight arrays of the experiment. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

To estimate the uncertainty on the depth of the source of the tremor, we computed the width of the stack of the envelopes of the cross-correlation functions at half the maximum of the peak. We then computed the associated depth difference using the 1D velocity model. As we computed the envelopes of the cross-correlation functions before stacking, the peak is large and also the associated uncertainty on the depth. Nevertheless, about 75\% of the data points have an uncertainty under 8km (Figure 5). The uncertainties are higher for the Burnt Hill array, and are almost always lower than 8km for the five other arrays. We tried different stacking methods, both for the stacking of the correlation functions over all the seismic stations of a given array, and for the stacking of the envelopes of those stacks over the one-minute-long time windows when tremor is detected. We experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack, and found that using a phase-weighted stack for both the stacking over the stations and the stacking over one-minute-long time windows gave the lower uncertainty on the tremor depth. \\

@@

In the following, we kept only the data points for which the maximum amplitude of the stack is higher than 0.05. Figures 6 and 7 show respectively a map and three cross-sections of the depth of the source of the tremor. Figure 8 shows a map of the distance between the source of the tremor and the plate boundary from the Preston model, alongside with the depth of the low-frequency earthquake families observed by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}. There is a good agreement between the depth of the source of the tremor, the depth of the low-frequency earthquake families, and the depth of the plate boundary. On the cross-section figures, we compare the distance of the source of the tremor to the plate boundary for different locations of the cross-section. We note that the depth of the tremor matches well the depth of the low-frequency earthquakes. \\

@@

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor is larger than the depth range of the low-frequency earthquakes, but it may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR} to locate the low-frequency earthquake families. \\

@@

We developed a method to estimate the depth of the source of the tectonic tremor, and the depth extent of the region from which the tremor originates, using S minus P times determined from lag times of stacked cross-correlations of horizontal and vertical components of seismic recordings from small aperture arrays in the Olympic Peninsula, Washington. We found that the source of the tremor is located close to the plate boundary in a region no more than 2-3 kilometers thick. The source of the tremor is thus distributed over a slightly wider depth range than the low-frequency earthquakes. However, due to the depth uncertainty, it is difficult to conclude whether the tremor is located near the top  of the subducting oceanic crust, in the lower continental crust just above the plate boundary, in a layer distributed above and below the plate boundary, or confined to a very narrow plate boundary. The location of the tremor relative to the low-velocity layer also observed near the plate boundary also remains uncertain.  Tremor and LFE depths are consistent with filling a volume in the upper subducted crust that is characterized by high fluid pressure and very low S-wave velocities described as the preferred model by ~\citeA{BOS_2013}. \\

The results presented here are related to a self-consistent 3-D P-wave velocity model and simultaneously determined plate interface model ~\cite{PRE_2003}. This model was used to determine tremor epicenters ~\cite{GHO_2012} and the LFE locations ~\cite{SWE_2019, CHE_2017_JGR} along with an assumed Vp / Vs ratio of 1.73.  The tremor depths in this study were determined using the 3-D model of ~\citeA{MER_2020}. They used the Preston model as a starting model and used P and S arrival times at source-receiver pairs to constrain the S-wave velocity.

@@

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/timelags}.
